Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-13 paper_comparison/paper_comparison/paper_comparison.tex
regroup sections

@@

Visual inference was first introduced in a 1999 Joint Statistical
Meetings (JSM) talk with the title ``Inference for Data Visualization''
by \citet{buja_inference_1999} as an idea to address the issue of valid
inference for visual discoveries of data plots
\citep{gelman_exploratory_2004}. Later, \citet{buja_statistical_2009}
proposed the lineup protocol as a visual test inspired by the ``police
lineup'' or ``identity parade'' which is the act of asking the
eyewitness to identify criminal suspect from a group of irrelevant
people. The protocol consists of \(m\) randomly placed plots, where one
plot is the actual data plot, and the remaining \(m - 1\) plots have the
identical graphical production as the data plot except the data has been
replaced with data consistent with the null hypothesis. Then, an
observer who have not seen the actual data plot will be asked to point
out the most different plot from the lineup. Figure
\ref{fig:first-example-lineup} is an example of a lineup protocol. If
the actual data plot at position 11 is identifiable, then it is evidence
for the rejection of the null hypothesis that the regression model is
correctly specified. In fact, the actual residual plot is obtained from
a misspecified regression model with non-linearity issue.

Data used in the \(m - 1\) null plots needs to be simulated. In the
context of regression diagnostics, sampling data from \(H_0\) is
equivalent to sampling data from the assumed model. As
\citet{buja_statistical_2009} suggested, \(H_0\) is usually composited
by a collection of distributions controlled by nuisance parameters.
Since regression models can have various forms, there is no general
solution to this problem, but it sometimes can be reduced to so called
``reference distribution'' by applying one of the three methods: (i)
sampling from a conditional distribution given a minimal sufficient
statistic under \(H_0\), (ii) parametric bootstrap sampling with
nuisance parameters estimated under \(H_0\), and (iii) Bayesian
posterior predictive sampling. The conditional distribution given a
minimal sufficient statistic is the best justified reference
distribution among the three \citep{buja_statistical_2009}. Essentially,
null residuals can be simulated by regressing \(N\) i.i.d standard
normal random draws on the regressors, then rescaling it by the ratio of
residual sum of square in two regressions.

@@

>>>>

\hypertarget{lineup-protocol}{%
\subsubsection{Lineup protocol}\label{lineup-protocol}}

@@

Visual inference was first introduced in a 1999 Joint Statistical
Meetings (JSM) talk with the title ``Inference for Data Visualization''
by \citet{buja_inference_1999} as an idea to address the issue of valid
inference for visual discoveries of data plots
\citep{gelman_exploratory_2004}. Later, \citet{buja_statistical_2009}
proposed the lineup protocol as a visual test inspired by the ``police
lineup'' or ``identity parade'' which is the act of asking the
eyewitness to identify criminal suspect from a group of irrelevant
people. The protocol consists of \(m\) randomly placed plots, where one
plot is the actual data plot, and the remaining \(m - 1\) plots have the
identical graphical production as the data plot except the data has been
replaced with data consistent with the null hypothesis. Then, an
observer who have not seen the actual data plot will be asked to point
out the most different plot from the lineup. Under the null hypothesis,
it is expected that the actual data plot would have no distinguishable
difference with the null plots, and the probability of the observer
correctly picks the actual data plot is \(1/m\). If we reject the null
hypothesis as the observer correctly picks the actual data plot, then
the Type I error of this test is \(1/m\).

@@

Figure \ref{fig:first-example-lineup} is an example of a lineup
protocol. If the actual data plot at position 11 is identifiable, then
it is evidence for the rejection of the null hypothesis that the
regression model is correctly specified. In fact, the actual residual
plot is obtained from a misspecified regression model with non-linearity
issue.

\hypertarget{sampling-from-the-null-distribution}{%
\subsubsection{Sampling from the null
distribution}\label{sampling-from-the-null-distribution}}

Data used in the \(m - 1\) null plots need to be simulated. In the
context of regression diagnostics, sampling data from \(H_0\) is
equivalent to sampling data from the assumed model. As
\citet{buja_statistical_2009} suggested, \(H_0\) is usually composited
by a collection of distributions controlled by nuisance parameters.
Since regression models can have various forms, there is no general
solution to this problem, but it sometimes can be reduced to so called
``reference distribution'' by applying one of the three methods: (i)
sampling from a conditional distribution given a minimal sufficient
statistic under \(H_0\), (ii) parametric bootstrap sampling with
nuisance parameters estimated under \(H_0\), and (iii) Bayesian
posterior predictive sampling. The conditional distribution given a
minimal sufficient statistic is the best justified reference
distribution among the three \citep{buja_statistical_2009}. Essentially,
null residuals can be simulated by regressing \(N\) i.i.d standard
normal random draws on the regressors, then rescaling it by the ratio of
residual sum of square in two regressions.

\hypertarget{p-value-calculation}{%
\subsubsection{p-value calculation}\label{p-value-calculation}}
